TORs2 and 3

### 2024-02-05 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
working on presentation
example syntax for creating figure, pulling in existing figure, and printing table

---
title: "TORs2 and 3"
output: beamer_presentation
slide_level: 3
theme: "Darmstadt"
logo: WHOI_NOAA_logo_smaller.png
date: "2024-02-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

## Stock parameters

- make some plots of maturity at age, weight at age, true deterministic SRR

@@

-- make some plots of fishery and index selectivity at age, q-index

@@

- make some plots to illustrate OM inputs and resulting simulated data generated

@@

- simple table listing EMs

>>>>

---
title: "TORs2 and 3"
output: beamer_presentation
fig_caption: FALSE
slide_level: 3
theme: "Darmstadt"
titlegraphic: WHOI_NOAA_logo_smaller.png
date: "`r Sys.Date()`"
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

## Stock parameters for generic gadid

```{r , echo=FALSE, message=FALSE, warnings=FALSE, results='hide'}
library(patchwork)
library(tidyverse)
library(wham)
naa_om_inputs <- readRDS(file.path(here::here(),"Project_0","inputs", "NAA_om_inputs.RDS"))
om.data <- naa_om_inputs[[1]]$data
mat.waa <- as_tibble(cbind(Age=seq(1, om.data$n_ages), WAA=om.data$waa[1,1,], Mat = om.data$mature[1,] ))
temp <- fit_wham(naa_om_inputs[[1]], do.fit = FALSE, MakeADFun.silent = TRUE)
SRab <- exp(c(temp$rep$log_SR_a[1], temp$rep$log_SR_b[1]))
srr <- as_tibble(cbind(SSB=seq(0,3.5e5, length=1000), Recruits= (SRab[1]*seq(0,3.5e5, length=1000)/(1+SRab[2]*seq(0,3.5e5, length=1000)) )  ))

mat.plot <- ggplot(mat.waa, aes(x=Age, y=Mat)) +
  geom_line(linewidth=1) +
  geom_point(size=2.5) +
  ylab('Maturity at age') +
  scale_x_continuous(breaks=mat.waa$Age, labels=as.character(mat.waa$Age))+
  theme(axis.text.x = element_text(size = 15))   + 
  theme(axis.text.y = element_text(size = 15)) +
  theme(axis.title.x = element_text(size = 16))   + 
  theme(axis.title.y = element_text(size = 16))  
ggsave(mat.plot, filename=file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation','plots', 
                           'mat.plot.png'), height=3, width=4)
waa.plot <- ggplot(mat.waa, aes(x=Age, y=WAA)) +
  geom_line(linewidth=1, color='blue') +
  geom_point(size=2.5, color='blue') +
  ylab('Weight at age (SSB and Catch)') +
  scale_x_continuous(breaks=mat.waa$Age, labels=as.character(mat.waa$Age))  +
  theme(axis.text.x = element_text(size = 15))   + 
  theme(axis.text.y = element_text(size = 15))  + 
  theme(axis.title.y = element_text(size = 16))  + 
  theme(axis.title.x = element_text(size = 16))  
ggsave(waa.plot, filename=file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation','plots', 
                           'waa.plot.png'), height=3, width=4)

srr.plot <- ggplot(srr, aes(x=SSB, y=Recruits)) +
  geom_line(linewidth=1, color='red')  +
  theme(axis.text.x = element_text(size = 15))   + 
  theme(axis.text.y = element_text(size = 15))  + 
  theme(axis.title.y = element_text(size = 16))  + 
  theme(axis.title.x = element_text(size = 16))  
  # geom_point(size=2.5, color='blue') +
  # ylab('Weight at age (SSB and Catch)')
ggsave(srr.plot, filename=file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation','plots', 
                           'srr.plot.png'), height=3, width=8)

bio.plot <- (mat.plot|waa.plot)/srr.plot
# ggsave(bio.plot, filename=file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation','plots', 'bio.plot.png'),  height=7, width=8)

plot(bio.plot)
```
<!-- knitr::include_graphics("bio.plot.png") -->
<!-- \includegraphics{file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation','plots', 'bio.plot.pdf')} -->
<!-- - make some plots of maturity at age, weight at age, true deterministic SRR -->

@@

<!-- -- example chunk to include figure from file -->
```{r,  echo=FALSE, message=FALSE, warnings=FALSE, results='hide', out.width='75%', fig.align='center'}
gf_info = make_basic_info()

#selectivity is not changing
gf_selectivity <- list(model       =c(rep("logistic", gf_info$n_fleets),rep("logistic", gf_info$n_indices)),
                       initial_pars=rep(list(c(5,1)), gf_info$n_fleets + gf_info$n_indices)) #fleet, index

a50 = gf_selectivity$initial_pars[[1]][1]
k= gf_selectivity$initial_pars[[1]][2]
sel.tmp <- 1.0/(1.0 + exp(-(seq(1, om.data$n_ages) - a50)/k))
sel <- sel.tmp/sel.tmp[om.data$n_ages]
fish.sel <- as_tibble(cbind(Age=seq(1, om.data$n_ages), Sel=sel))
ggplot(fish.sel, aes(x=Age, y=Sel)) + 
  geom_line(color='green4', linewidth=1) +
  geom_point(color='green4', size=2.5) +
  ylab('Fishery Selectivity at Age') +
  theme(axis.text.x = element_text(size = 15))   + 
  theme(axis.text.y = element_text(size = 15))  + 
  theme(axis.title.y = element_text(size = 16))  + 
  theme(axis.title.x = element_text(size = 16))

```

@@

<!-- -- example chunk to include figure from file -->
```{r, out.width='25%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'model_probability_beta_fix.png') )
```

- make some plots to illustrate OM inputs and resulting simulated data generated
- looks like i can have multiple bullets below a figure

@@

- simple bullets above table
- we only have 6 EMs that were considered

```{r,  echo=FALSE, message=FALSE, warnings=FALSE}

df.ems    <- readRDS(file.path(here::here(),"Ecov_study", "recruitment_functions", "inputs", "df.ems.RDS"))

em_tib <- as_tibble(df.ems) %>%
  mutate(SR=ifelse(r_mod==2, 'Mean', 'BH')) %>%
  mutate(EM_mod = paste0(SR, "_", ecov_how), EM=seq(1,6))

   knitr::kable(em_tib)
  # print(em_tib)

```
